---
title: "varexternalinstrument"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{varexternalinstrument}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Basic usage

The library is designed to work with the R `vars` package, though an interface is available to work with a generic set of reduced form residuals.

The package includes the replication data from Gertler Karadi (the original data can be found [here](https://www.aeaweb.org/aej/mac/data/0701/2013-0329_data.zip)). 

The library integrates easily with the `vars` package. The following example illustrates how to replicate the main result from Gertler and Karadi (2015).

```{r warning=FALSE, message=FALSE}
library(vars)
library(varexternalinstrument)

data(GKdata)

gkvar <- VAR(GKdata[, c("logip", "logcpi", "gs1", "ebp")], p = 12, type = "const")
shockcol <- externalinstrument(gkvar, GKdata$ff4_tc, "gs1")
shockcol
```

The result, `shockcol` contains the instaneous response of each of the variables in the VAR to a shock to `gs1` (in this case, the monetary policy indicator). This can then be used to create IRFs, etc.

### Creating IRFs

Here I use the `Phi` function from the `vars` package, which gives the moving average representation of an estimated
var over a given finite horizon. I construct 20 period IRFs, mimicking figure 1 from Gertler & Karadi (2015).

```{r warning=FALSE, message=FALSE}
library(tidyr)
library(dplyr)
library(ggplot2)
ma_representation <- Phi(gkvar, 50)
irfs <- apply(ma_representation, 3, function(x) x %*% shockcol)
irfs <- as.data.frame(t(irfs))
colnames(irfs) <- names(shockcol)
irfs <- mutate(irfs, horizon = 0:50)
irfs <- gather(irfs, key = variable, value = response, -horizon)
ggplot(irfs, aes(x = horizon, y = response, group = variable, color = variable)) + geom_line()
```
